Technical Report

### 2018-04-04 fully-abstract-comp/technical-report.tex
Proposed change to seal case in untrusted value relation.
Requirement on all seals in range of available seals rather than on the specific seal pointed to.
added a suggestion for permission-based conditions using adjacent regions.
proposed update to execCond to handle subseg operation
resolved TODO about stack base address in memsat and main optional

\begin{definition}[Programs and Contexts]
  We define a program $(\var{comp}, c_{\mathrm{main},c}, c_{\mathrm{main},d})$ as a component with an empty import list and $c_{\mathrm{main},c}$ and $c_{\mathrm{main},d}$ are two of the exported symbols.

  Given a component $\var{comp}$, a context is a tuple $(\var{comp'}, c_{\mathrm{main},c}, c_{\mathrm{main},d})$ such that $\var{comp'}$ is a component and $(\var{comp} \bowtie \var{comp'}, c_{\mathrm{main},c}, c_{\mathrm{main},d})$ is a program.
\end{definition}

@@

\[
  \memSatFStack{ms_\stk,\ms_T}{W} \text{ iff } 
  \left\{
    \begin{array}{l}
      W_\var{stack} = \pwfree \wedge \\
      \exists R_\ms : \dom(\activeReg{W_\var{stack}}) \fun \MemSeg \times \MemSeg \wedge \\
      \quad \ms_T = \biguplus_{r \in \dom(\activeReg{W_\var{stack}})} \pi_2(R_\ms(r)) \wedge \\
      \quad \ms_\stk = \biguplus_{r \in \dom(\activeReg{W_\var{stack}})} \pi_1(R_\ms(r)) \wedge \\
      \quad \exists R_W : \dom(\activeReg{W_\var{stack}}) \fun \World\ldotp\\
      \qquad W = \oplus_{r \in \dom(\activeReg{W_\var{stack}})} R_W(r) \wedge\\
      \qquad \forall r \in \dom(\activeReg{W_\var{stack}}) \ldotp \\
      \qquad \quad \npair{R_\ms(r)} \in  W_\var{stack}(r).H \; \xi^{-1}(R_W(r))
    \end{array}
  \right.
\]

@@

      % This case was never used (?) so it is not necessary.
      % \wedge \\
      % \quad \npair[n']{\src{\vsc_S'},\src{\vsc_S},\vsc_T',\vsc_T} \in \lrexj(W' \oplus W_o)
    \end{array}
    \right\}\cup\\
    \left\{ \npair{\left(\arraycolsep=0pt\array{l} \src{\seal{\sigma,\sigma_\baddr,\sigma_\eaddr}},\\ \seal{\sigma,\sigma_\baddr,\sigma_\eaddr} \endarray \right)} 
    \; \middle| \;
    \exists r \in \dom(\pwheap) \ldotp \pwheap(r) = (\pure,\_,H_\sigma) \tand H_\sigma \; \sigma \nequal \lrv
    \right\} \cup \\
    \left\{ \npair{\left(\arraycolsep=0pt\array{l} \src{\stkptr{\perm,\baddr,\eaddr,\aaddr}},\\ ((\perm,\linear),\baddr,\eaddr,\aaddr) \endarray \right)} \;\middle|\;
    \begin{array}{l}
      \begin{array}{r l l}
        \perm = \noperm & \Rightarrow & \npair{(\linear,\baddr,\eaddr)} \in \lrp(W) \wedge \\
        \perm \in \readAllowed{} &\Rightarrow& \npair{(\baddr,\eaddr)} \in \stackReadCond{W} \wedge \\
        \perm \in \writeAllowed{} &\Rightarrow& \npair{(\baddr,\eaddr)} \in \stackWriteCond{W}
      \end{array}
    \end{array}
    \right\} \cup \\
%
    \left\{ \npair{\left(\arraycolsep=0pt\array{l} \src{((\perm,\lin),\baddr,\eaddr,\aaddr)},\\ ((\perm,\lin),\baddr,\eaddr,\aaddr) \endarray \right)} \;\middle|\; 
    \begin{array}{l}
      \begin{array}{r l l }
        \perm = \noperm & \Rightarrow & \npair{(\lin,\baddr,\eaddr)} \in \lrp(W) \wedge \\
        \perm \in \readAllowed{} &\Rightarrow& \npair{(\baddr,\eaddr)} \in \readCond{\lin,W} \wedge\\
        \perm \in \writeAllowed{} &\Rightarrow& \npair{(\baddr,\eaddr)} \in \writeCond{\lin,W} \wedge\\
        % we are excluding rwx pointers.
        \perm \neq \rwx \wedge \\
        % \perm = \rwx &\Rightarrow& \array[t]{l}\npair{(\{\rwx,\rx\},\baddr,\eaddr)} \in \execCond{\lin,W} \wedge \\
        %                            \npair{(\baddr,\eaddr)} \in \xReadCond{\lin,W} \endarray\\
        \perm = \rx &\Rightarrow& \array[t]{l}\npair{(\{\rx\},\baddr,\eaddr)} \in \execCond{\lin,W} \wedge\\
                                  \npair{(\baddr,\eaddr)} \in \xReadCond{\lin,W}\endarray
      \end{array}
    \end{array}
    \right\}
  \end{array}
\]

@@

\[
  \readCond{\lin,W} = \left\{ \npair{(\baddr,\eaddr})) \middle| 
    \begin{array}{l}
      \exists r \in \addressable{\lin, \pwheap} \ldotp \\
      \quad \exists A \supseteq [\baddr,\eaddr] \ldotp \\
      \qquad \pwheap(r) \nsubeq \stdreg{A,\gc}{\pur}
    \end{array}
  \right\}
\]
\lau{TODO: Make this condition require a set of adjacent regions. Check whether needed for the stack condition.}
where $\iota_A$ is a standard region defined in Section~\ref{sec:standard-regions}.
\[
  \stackReadCond{W} = \left\{ \npair{(\baddr,\eaddr})) \middle| 
    \begin{array}{l}
      \exists r \in \addressable{\linear, \pwfree} \ldotp \\
      \quad \exists [\baddr',\eaddr'] \supseteq [\baddr,\eaddr] \ldotp \\
      \qquad \pwfree(r) \nsubeq \stdreg{[\baddr',\eaddr'],\gc}{\pur}
    \end{array}
  \right\}
\]
where $\iota_A$ is a standard region defined in Section~\ref{sec:standard-regions}.
\[
  \xReadCond{\lin,W} = \left\{ \npair{(\baddr,\eaddr})) \middle| 
    \begin{array}{l}
      \exists r \in \addressable{\lin, \pwheap}, \sigrets, \sigcloss, \code  \ldotp\\
      \quad \dom(\ms) \supseteq [\baddr,\eaddr] \wedge \\
      \quad \pwheap(r) \nequal \codereg{\sigrets,\sigcloss,\code,\gc}
    \end{array}
  \right\}
\]
\lau{TODO: Make this condition require a set of adjacent regions.}
\lau{TODO: allow code regions to be merged into one. Allow for (... forgot to write the rest, but probably related to splicing regions.) }
\dominique{9-3-2018: I changed the above to require that $\ms$ contains safe values by requiring that it is in Hstd. Is this reasonable?}

@@

\[
  \writeCond{\lin,W} = \left\{ \npair{(\baddr,\eaddr)}) \middle| 
    \begin{array}{l}
      \exists r \in \addressable{\lin, \pwheap} \ldotp \\
      \quad \exists [\baddr',\eaddr'] \supseteq [\baddr,\eaddr] \ldotp \\
      \qquad \pwheap(r) \nsupeq[n-1] \stdreg{[\baddr',\eaddr'],\gc}{\pur} \wedge \\
      \qquad \pwheap(r) \text{ is address-stratified}
    \end{array}
  \right\}
\]
\lau{TODO: Make this condition require a set of adjacent regions. Check whether necessary for the stack region.}
where $\iota_A$ is a standard region defined in Section~\ref{sec:standard-regions}.
\dominique{Why $n-1$ above?  There is already a quantification over $n' <n$ in the memory satisfaction relation and another $n-1$ is used in $\stdreg{[\baddr',\eaddr'],\gc}{\pur}$. Also: readCond doesn't have the $n-1$.}
\[
  \stackWriteCond{W} = \left\{ \npair{(\baddr,\eaddr)}) \middle| 
    \begin{array}{l}
      \exists r \in \addressable{\linear, \pwfree} \ldotp \\
      \quad \exists [\baddr',\eaddr'] \supseteq [\baddr,\eaddr] \ldotp \\
      \qquad \pwfree(r) \nsupeq[n-1] \stdreg{[\baddr',\eaddr'],\gc}{\pur} \wedge \\
      \qquad \pwfree(r) \text{ is address-stratified}
    \end{array}
  \right\}
\]
where $\iota_A$ is a standard region defined in Section~\ref{sec:standard-regions}.

@@

% \dominique{22-1-2018: the below is an alternative proposal to the above definition. It is part of a proposed refactoring to simplify the merge the cases for return pointers and closures in the value relation.}
Note: this new version of execCond uses the expression relation for regular jumps since it expresses the validity of jumping to an address pointed to by an executable capability. 
\[
  \execCond{\lin,W} = \left\{ \npair{(S_\perm,\baddr,\eaddr)} \middle|
    \begin{array}{l}
      \forall W_l \ldotp\\
      \quad ((W_l = \purePart{W} \wedge \lin = \normal) \vee (W_l = W \wedge \lin = \linear)) \wedge\\
      \quad \forall n' < n, W' \future W_l, \perm \in S_\perm, \aaddr \in [\baddr,\eaddr] \ldotp\\
      \qquad \npair[n']{\stpair[.]{((\perm,\lin),\baddr,\eaddr,\aaddr)}{((\perm,\lin),\baddr,\eaddr,\aaddr)}} \in \lre(W')
    \end{array}
    \right\}
\]

\subsection{Standard regions}
\label{sec:standard-regions}
Standard region:
\[
  \stdreg{A,\gc}{v} \defeq (v,H_A^{\mathrm{std},\square} \; \gc)
\]
for readability, we use $\spao$ short for $\spatialo$, $\spa$ short for $\spatial$, and $\pur$ as short for $\pure$.
\lau{02-11-2017: I am not sure whether it should be a $\normal$ region. In previous work $\nsubeq$ ignored the ``view'' which it may also do here, and then then it does not matter which one it is.}
where $H_A$ is defined as follows:
\[
  H_A^{\mathrm{std},\square} \; \gc \; \hat{W} \defeq \left\{ \npair{\ms_S,\ms_T} \middle|
    \begin{array}{l}
      \dom(\ms_S) = \dom(\ms_T) = A \wedge \\
      \exists S : A \fun \World \ldotp \xi(W) = \oplus_{\aaddr \in A} S(\aaddr) \wedge\\
      \quad \forall \aaddr \in A \ldotp \npair[n-1]{(\ms_S(\aaddr),\ms_T(\aaddr))} \in \lrv(S(\aaddr))
    \end{array}
  \right\}
\]
\lau{01-11-2017: TODO look into what kind of world separation should happen here.}
\dominique{7-3-2018: is it necessary to have $n-1$ above? there is already a quantification over $n'<n$ in the memory satisfaction relation.}

@@

\section{Full Abstraction}
\lau{TODOs from last day in Leuven}
\lau{TODO: components have optional main (pc/data pair)}
\lau{TODO: linking component and context requires only one main (i.e., it is undefined if both or none of the two expose main.)}
\lau{TODO: Component logical relation.}
\lau{TODO: Version of FTLR for programs.}
\lau{TODO: Component lemma for initial executable configurations.}
\lau{TODO: Executable configuration lemma.}
\lau{TODO: ... should use initial executable configuration.}
\lau{TODO: Did we agree that memory satisfaction should require $\stkb$ to be a free stack address (or at least not in the heap part)? I think we did.}
\begin{definition}
  \label{def:points-to-instr}
  A configuration $(\ms,\reg)$ {\sourcecolor or $\Phi = (\ms,\reg,\_,\_)$} is said to point to non-$\scall{}{}{}$ instruction $i$ in $A$ iff
  \[
    \reg(\pcreg) = ((\_,\_),\_,\eaddr,\aaddr) \tand \aaddr \in A
  \]
and
\[
  \decInstr{\ms(\aaddr)} = i
\]
\end{definition}

>>>>

\begin{definition}[Programs and Contexts]
  We define a program to be either a component $\var{comp}$ or a tuple $(\var{comp}, c_{\mathrm{main},c}, c_{\mathrm{main},d})$ with component $\comp$ with an empty import list and $c_{\mathrm{main},c}$ and $c_{\mathrm{main},d}$ are two of the exported symbols.

A context is a program defined as above.
% Given a component $\var{comp}$, a context is a tuple $(\var{comp'}, c_{\mathrm{main},c}, c_{\mathrm{main},d})$ such that $\var{comp'}$ is a component and $(\var{comp} \bowtie \var{comp'}, c_{\mathrm{main},c}, c_{\mathrm{main},d})$ is a program.

Two programs $\var{comp}$ and $(\var{comp}', c_{\mathrm{main},c}, c_{\mathrm{main},d})$ can be linked into a new program $(\var{comp} \bowtie \var{comp'}, c_{\mathrm{main},c}, c_{\mathrm{main},d})$.
\end{definition}

@@

\[
  \memSatFStack{ms_\stk,\ms_T}{W} \text{ iff } 
  \left\{
    \begin{array}{l}
      W_\var{stack} = \pwfree \wedge \\
      \exists R_\ms : \dom(\activeReg{W_\var{stack}}) \fun \MemSeg \times \MemSeg \wedge \\
      \quad \ms_T = \biguplus_{r \in \dom(\activeReg{W_\var{stack}})} \pi_2(R_\ms(r)) \wedge \\
      \quad \ms_\stk = \biguplus_{r \in \dom(\activeReg{W_\var{stack}})} \pi_1(R_\ms(r)) \wedge \\
      \quad \stkb \in \dom(\ms_T) \wedge \stkb \in \dom(\ms_\stk) \wedge \\
      \quad \exists R_W : \dom(\activeReg{W_\var{stack}}) \fun \World\ldotp\\
      \qquad W = \oplus_{r \in \dom(\activeReg{W_\var{stack}})} R_W(r) \wedge\\
      \qquad \forall r \in \dom(\activeReg{W_\var{stack}}) \ldotp \\
      \qquad \quad \npair{R_\ms(r)} \in  W_\var{stack}(r).H \; \xi^{-1}(R_W(r))
    \end{array}
  \right.
\]

@@

      % This case was never used (?) so it is not necessary.
      % \wedge \\
      % \quad \npair[n']{\src{\vsc_S'},\src{\vsc_S},\vsc_T',\vsc_T} \in \lrexj(W' \oplus W_o)
    \end{array}
    \right\}\cup\\
    \left\{ \npair{\left(\arraycolsep=0pt\array{l} \src{\seal{\sigma,\sigma_\baddr,\sigma_\eaddr}},\\ \seal{\sigma,\sigma_\baddr,\sigma_\eaddr} \endarray \right)} 
    \; \middle| \;
    \begin{array}{l}
      \exists r \in \dom(\pwheap) \ldotp \\
      \quad \forall \sigma' \in [\sigma_\baddr,\sigma_\eaddr] \ldotp\pwheap(r) = (\pure,\_,H_\sigma) \tand H_\sigma \; \sigma' \nequal \lrv
    \end{array}
    \right\} \cup \\
    \left\{ \npair{\left(\arraycolsep=0pt\array{l} \src{\stkptr{\perm,\baddr,\eaddr,\aaddr}},\\ ((\perm,\linear),\baddr,\eaddr,\aaddr) \endarray \right)} \;\middle|\;
    \begin{array}{l}
      \begin{array}{r l l}
        \perm = \noperm & \Rightarrow & \npair{(\linear,\baddr,\eaddr)} \in \lrp(W) \wedge \\
        \perm \in \readAllowed{} &\Rightarrow& \npair{(\baddr,\eaddr)} \in \stackReadCond{W} \wedge \\
        \perm \in \writeAllowed{} &\Rightarrow& \npair{(\baddr,\eaddr)} \in \stackWriteCond{W}
      \end{array}
    \end{array}
    \right\} \cup \\
%
    \left\{ \npair{\left(\arraycolsep=0pt\array{l} \src{((\perm,\lin),\baddr,\eaddr,\aaddr)},\\ ((\perm,\lin),\baddr,\eaddr,\aaddr) \endarray \right)} \;\middle|\; 
    \begin{array}{l}
      \begin{array}{r l l }
        \perm = \noperm & \Rightarrow & \npair{(\lin,\baddr,\eaddr)} \in \lrp(W) \wedge \\
        \perm \in \readAllowed{} &\Rightarrow& \npair{(\baddr,\eaddr)} \in \readCond{\lin,W} \wedge\\
        \perm \in \writeAllowed{} &\Rightarrow& \npair{(\baddr,\eaddr)} \in \writeCond{\lin,W} \wedge\\
        % we are excluding rwx pointers.
        \perm \neq \rwx \wedge \\
        % \perm = \rwx &\Rightarrow& \array[t]{l}\npair{(\{\rwx,\rx\},\baddr,\eaddr)} \in \execCond{\lin,W} \wedge \\
        %                            \npair{(\baddr,\eaddr)} \in \xReadCond{\lin,W} \endarray\\
        \perm = \rx &\Rightarrow& \array[t]{l}\npair{(\{\rx\},\baddr,\eaddr)} \in \execCond{\lin,W} \wedge\\
                                  \npair{(\baddr,\eaddr)} \in \xReadCond{\lin,W}\endarray
      \end{array}
    \end{array}
    \right\}
  \end{array}
\]

@@

\[
  \readCond{\lin,W} = \left\{ \npair{(\baddr,\eaddr})) \middle| 
    \begin{array}{l}
      \exists S \subseteq \addressable{\lin, \pwheap} \ldotp \\
      \quad \exists R : S \fun \powerset{\nats} \\
      \qquad \biguplus_{r\in S} R(r) \supseteq [\baddr,\eaddr] \wedge\\
      \qquad \quad \forall r \in S \ldotp \pwheap(r) \nsubeq \stdreg{R(r),\gc}{\pur}
    \end{array}
  \right\}
\]
\lau{RESOLVED: Make this condition require a set of adjacent regions. Check whether needed for the stack condition.}
where $\iota_A$ is a standard region defined in Section~\ref{sec:standard-regions}.
\[
  \stackReadCond{W} = \left\{ \npair{(\baddr,\eaddr})) \middle| 
    \begin{array}{l}
      \exists S \subseteq \addressable{\lin, \pwfree} \ldotp \\
      \quad \exists R : S \fun \powerset{\nats} \\
      \qquad \biguplus_{r\in S} R(r) \supseteq [\baddr,\eaddr] \wedge \\
      \qquad \quad \forall r \in S \ldotp \pwfree(r) \nsubeq \stdreg{R(r),\gc}{\pur}
    \end{array}
  \right\}
\]
where $\iota_A$ is a standard region defined in Section~\ref{sec:standard-regions}.
\[
  \xReadCond{\lin,W} = \left\{ \npair{(\baddr,\eaddr})) \middle| 
    \begin{array}{l}
      \exists S \subseteq \addressable{\lin, \pwfree} \ldotp \\
      \quad \exists M : S \fun \powerset{\MemSeg}, R : S \fun \powerset{\Seal}, C : S \fun \powerset{\Seal} \\
      \qquad \biguplus_{r\in S} \dom(M(r)) \supseteq [\baddr,\eaddr] \wedge\\
      \qquad \biguplus_{r\in S} R(r) \# \biguplus_{r\in S} C(r) \wedge \\
      \qquad \quad \forall r \in S \ldotp  \pwheap(r) \nequal \codereg{R(r),C(r),M(r),\gc}
    \end{array}
  \right\}
\]
\lau{RESOLVED: Make this condition require a set of adjacent regions.}
\lau{TODO: allow code regions to be merged into one. Allow for (... forgot to write the rest, but probably related to splicing regions.) }
\dominique{9-3-2018: I changed the above to require that $\ms$ contains safe values by requiring that it is in Hstd. Is this reasonable?}

@@

\[
  \writeCond{\lin,W} = \left\{ \npair{(\baddr,\eaddr)}) \middle| 
    \begin{array}{l}
      \exists S \subseteq \addressable{\lin, \pwheap} \ldotp \\
      \quad \exists R : S \fun \powerset{\nats} \\
      \qquad \biguplus_{r\in S} R(r) \supseteq [\baddr,\eaddr] \wedge\\
      \qquad \quad \forall r \in S \ldotp \pwheap(r) \nsupeq[n-1] \stdreg{R(r),\gc}{\pur} \wedge\\
      \qquad \quad \pwheap(r) \text{ is address-stratified}
    \end{array}
  \right\}
\]
\lau{TODO: Make this condition require a set of adjacent regions. Check whether necessary for the stack region.}
where $\iota_A$ is a standard region defined in Section~\ref{sec:standard-regions}.
\dominique{Why $n-1$ above?  There is already a quantification over $n' <n$ in the memory satisfaction relation and another $n-1$ is used in $\stdreg{[\baddr',\eaddr'],\gc}{\pur}$. Also: readCond doesn't have the $n-1$.}
\[
  \stackWriteCond{W} = \left\{ \npair{(\baddr,\eaddr)}) \middle| 
    \begin{array}{l}
      \exists S \subseteq \addressable{\lin, \pwfree} \ldotp \\
      \quad \exists R : S \fun \powerset{\nats} \\
      \qquad \biguplus_{r\in S} R(r) \supseteq [\baddr,\eaddr] \wedge \\
      \qquad \quad \forall r \in S \ldotp \pwfree(r) \nsupeq[n-1] \stdreg{R(r),\gc}{\pur} \wedge\\
      \qquad \quad \pwfree(r) \text{ is address-stratified}
    \end{array}
  \right\}
\]
where $\iota_A$ is a standard region defined in Section~\ref{sec:standard-regions}.

@@

% \dominique{22-1-2018: the below is an alternative proposal to the above definition. It is part of a proposed refactoring to simplify the merge the cases for return pointers and closures in the value relation.}
Note: this new version of execCond uses the expression relation for regular jumps since it expresses the validity of jumping to an address pointed to by an executable capability. 
\[
  \execCond{\lin,W} = \left\{ \npair{(S_\perm,\baddr,\eaddr)} \middle|
    \begin{array}{l}
      \forall W_l \ldotp\\
      \quad ((W_l = \purePart{W} \wedge \lin = \normal) \vee (W_l = W \wedge \lin = \linear)) \wedge\\
      \quad \forall n' < n, W' \future W_l, \perm \in S_\perm, \aaddr \in [\baddr',\eaddr'] \subseteq [\baddr,\eaddr] \ldotp\\
      \qquad \npair[n']{\stpair[.]{((\perm,\lin),\baddr',\eaddr',\aaddr)}{((\perm,\lin),\baddr',\eaddr',\aaddr)}} \in \lre(W')
    \end{array}
    \right\}
\]

\subsection{Standard regions}
\label{sec:standard-regions}
Standard region:
\[
  \stdreg{A,\gc}{v} \defeq (v,H_A^{\mathrm{std},\square} \; \gc)
\]
for readability, we use $\spao$ short for $\spatialo$, $\spa$ short for $\spatial$, and $\pur$ as short for $\pure$.
\lau{02-11-2017: I am not sure whether it should be a $\normal$ region. In previous work $\nsubeq$ ignored the ``view'' which it may also do here, and then then it does not matter which one it is.}
where $H_A$ is defined as follows:
\[
  H_A^{\mathrm{std},\square} \; \gc \; \hat{W} \defeq \left\{ \npair{\ms_S,\ms_T} \middle|
    \begin{array}{l}
      \dom(\ms_S) = \dom(\ms_T) = A \wedge \\
      \exists S : A \fun \World \ldotp \xi(W) = \oplus_{\aaddr \in A} S(\aaddr) \wedge\\
      \quad \forall \aaddr \in A \ldotp \npair[n-1]{(\ms_S(\aaddr),\ms_T(\aaddr))} \in \lrv(S(\aaddr))
    \end{array}
  \right\}
\]
\lau{01-11-2017: RESOLVED look into what kind of world separation should happen here.}
%\dominique{7-3-2018: is it necessary to have $n-1$ above? there is already a quantification over $n'<n$ in the memory satisfaction relation.} \lau{04-04-2018: The n'<n was removed from memory satisfaction.}

@@

\section{Full Abstraction}
\lau{TODOs from last day in Leuven}
\lau{RESOLVED: components have optional main (pc/data pair)}
\lau{RESOLVED?: linking component and context requires only one main (i.e., it is undefined if both or none of the two expose main.)}
\lau{TODO: Component logical relation.}
\lau{TODO: Version of FTLR for programs.}
\lau{TODO: Component lemma for initial executable configurations.}
\lau{TODO: Executable configuration lemma.}
\lau{TODO: ... should use initial executable configuration.}
\lau{TODO: Did we agree that memory satisfaction should require $\stkb$ to be a free stack address (or at least not in the heap part)? I think we did.}
\begin{definition}
  \label{def:points-to-instr}
  A configuration $(\ms,\reg)$ {\sourcecolor or $\Phi = (\ms,\reg,\_,\_)$} is said to point to non-$\scall{}{}{}$ instruction $i$ in $A$ iff
  \[
    \reg(\pcreg) = ((\_,\_),\_,\eaddr,\aaddr) \tand \aaddr \in A
  \]
and
\[
  \decInstr{\ms(\aaddr)} = i
\]
\end{definition}
